\LARGE \bf Geometric Adaptive Control of Attitude Dynamics on $\SO$\\ with State Inequality Constraints

### 2015-09-24 ACC16.2.tex
added figures and simulation plots. starting on experimental section

We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}
We assume a fixed disturbance of 
\begin{gather*}
	\Delta = \begin{bmatrix} 0.06 & 0.06 & 0.09 \end{bmatrix}^T \, ,
\end{gather*}
with the function \( W(R,\Omega) = I \).
This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
Present three cases

Show stabilization without repulsive term (passes through constraint)
Show stabilization with avoidance term without disturbance
Show stabilization with disturbance and adaptive update law

Plot of responses

Show rotation animation of spacecraft avoiding constrained regions

\section{Experiments}

Discuss experimental setup of the hexrotor on spherical joint

Describe aim of experiment. 
Demonstrate that hexrotor fixed sensor can stabilize to desired attitude while avoiding an obstacle.
Mount a sphere at an appropriate distance such that the subtended angle is equal to the cone constraint

@@

\subsection{Proof of }
Stability proofs for case with and without disturbance

Detail on finding bounds of \( \norm{\dot{e}_R} \)

Lots of intermediate terms

>>>>

We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}
We assume a fixed disturbance of 
\begin{gather*}
	\Delta = \begin{bmatrix} 0.06 & 0.06 & 0.09 \end{bmatrix}^T \, ,
\end{gather*}
with the function \( W(R,\Omega) = I \).
This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
\begin{figure}
	\includegraphics[width=\columnwidth]{cad}
	\caption{Trajectory in inertial frame\label{fig:cad}}
\end{figure}
\begin{figure} 
	\centering 
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{eR_con} 
		\caption{Attitude error vector \(e_R\) } \label{fig:eR_con} 
	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{eW_con} 
		\caption{Angular velocity error} \label{fig:eW_con} 
	\end{subfigure}

	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{Psi_con} 
		\caption{Configuration error \( \Psi \)} \label{fig:Psi_con} 
	\end{subfigure}~
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{u_con} 
		\caption{Control input \( u\)} \label{fig:u_con} 
	\end{subfigure} 
	\caption{Attitude stabilization without adaptive update law}
	\label{fig:con} 
\end{figure}

\begin{figure} 
	\centering 
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{eR_adapt} 
		\caption{Attitude error vector \(e_R\) } \label{fig:eR_adapt} 
	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{eW_adapt} 
		\caption{Angular velocity error} \label{fig:eW_adapt} 
	\end{subfigure}

	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{Psi_adapt} 
		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
	\end{subfigure}~
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{u_adapt} 
		\caption{Control input \( u\)} \label{fig:u_adapt} 
	\end{subfigure}

	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{Delta_adapt} 
		\caption{Disturbance estimate \( \bar{\Delta}\)} \label{fig:Delta_adapt} 
	\end{subfigure}
	\caption{Attitude stabilization with adaptive update law}
	\label{fig:adapt} 
\end{figure}

Simulation results without the adaptive update law are shown in~\cref{fig:con}.
Without the update law, the system does not achieve zero steady state error. 
\Cref{fig:Psi_con} shows that the configuration error function does not converge to zero.
\Cref{fig:adapt} shows the results with the addition of the adaptive update law.

The path of the body fixed sensor in the inertial frame is illustrated in~\cref{fig:cad}.
The initial attitude is represented with the green circle while the final attitude is marked with a green \(\times\).
The control system is able to asymptotically converge to zero attitude error.
In addition, the estimate of the disturbance converges to the the true value.
Both control system are able to automatically avoid the constrained regions. 
In addition, these results show that it is straightforward to incorporate an arbitrary amount of large constraints.
In spite of this challenging configuration space the proposed control system offers a simple method of avoiding constrained regions.
These closed-loop feedback results are computed in real time and offer a significant advantage over typical open-loop planning methods.
These results show that the proposed geometric adaptive approach is critical to attitude stabilization in the presence of state constraints and disturbances.

\section{Experiment on Hexrotor UAV}

A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory(FDCL) at the George Washington University.
The UAV is composed of three pairs of counter-rotating propellers. 
Typical quadrotor UAVs are composed of four or more co-planar propellers.
As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
This allows the hexrotor to impart a force in any direction and a moment about any axis. (cite hexrotor paper)

The hexrotor UAV is composed of the following parts:
\begin{itemize}
	\item ODROID processor 
	\item Wifi connectivity
	\item VectorNav IMU
	\item Vicon motion capture sent from command computer
\end{itemize}

Describe aim of experiment. 
Demonstrate that hexrotor fixed sensor can stabilize to desired attitude while avoiding an obstacle.s
Mount a sphere at an appropriate distance such that the subtended angle is equal to the cone constraint

@@
